\textsf{Are large language models superhuman chemists?}

### 2024-03-20 src/tex/ms.tex
need to think a bit about how to phrase conclusions

>>>>

The current evaluation frameworks for \glspl{llm} are mostly designed to measure the performance of the models on specific tasks. 
They cannot easily be used to evaluate systems, or models built for scientific applications. Thus, we had on little understanding of the capabilities of \glspl{llm} in the chemical sciences.
Our work,  shows that carefully curated benchmarks can provide a more nuanced understanding of the capabilities of \glspl{llm} in the chemical sciences.
It lays the groundwork for the development of more advanced systems that can be used in the chemical sciences and highlights the importance of continued development of evaluation frameworks for systematic improvement of safe and useful \glspl{llm}.
